Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-20 Cover_letter_JPM.tex
Answer 2-3 done
lasso

\subsection*{2-3}
% [2021/06/17]
% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity (less biomarkers but more P value < 1e-5?)

@@

% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
%
% [2021/06/13-17]
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11.
There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
%In the consensus of TCGA and GSE65858 cohorts,

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We appreciate the reviewer for the critical comments.
***  a gene signature with deep learning CNN,
or http://gepia2.cancer-pku.cn/#index
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
or 
Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.

>>>>

\subsection*{2-3}
% (OK)
% [2021/06/17]
% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity (less biomarkers but more P value < 1e-5?)

@@

% problem of it (少 n=30, and RFS only: validation rate 14/100 而且 10% cutoff)
%x Prognoscan (GSE2837) (n=30 less)  RFS only:  10\% cutoff to yield a \textit{P}-value < 0.05.\\
%找出  3 candidates
During our exploration phase with TCGA cohort, the 20 genes, listed
%six overexpressed genes (symbol as CAMK2N1, PGK1, SURF4, USP10, NDFIP1, FOXA2) are bad guy;
%four overexpressed genes (symbol as IL19, FCGBP, IQCN - former symbol as KIAA1683, and NPB) are good guy.
%}
in Figure \ref{fig:hazards3}, have FDR-adjusted \textit{P} values ($<0.001$) in Kaplan-Meier estimate, and survival impact on HR ($> 1.8$ or $< 0.6$) in Cox's model.
%
% [2021/06/13-17]
%CAMK2N1, IL19, and FCGBP is validated by
%candidate_fdr100
%PvalueTex consensus with GSE2837 to yield 3 candidates
In the study of GSE65858 cohort, CAMK2N1, IL19, and FCGBP, keep ahead of the curve by FDR-corrected \textit{P} value ($< 0.05$), and Cox'HR ($>1.8$ or $<0.65$) (please see Table \ref{tab:table_top3_GSE65858} listed below,
% (ok) (FDR KM \textit{P} value) <= # only MSMB KM FDR-adjusted P value = 0.002 
% Consensus 3 genes in Kaplan-Meier survival and Cox's model (dataset: GSE65858)
%Gene.Symbol KM.Pvalue   FDR.KMpvalue    uni_HR  FDR.Pvalue(in TCGA)
%CAMK2N1 0.00687 0.03782500  1.814   1.628308e-05
%FCGBP   0.01020 0.03886709  0.573   4.827833e-05
%IL19    0.03390   0.04738901    0.630   6.543871e-06
%IL19    0.00269  0.03068073 0.630  6.543871e-06
%candidate_fdr100
and also see Figure \ref{fig:hazards534}).
However, the "top rank" of the other 17 genes is replaced by genes such as DUSP6, MSMB, and RBM11 (please see Figure \ref{fig:hazards534}).
There is consensus between the TCGA and GSE65858 cohorts that CAMK2N1, IL19, and FCGBP are significant candidates for the biomarker.
%In the consensus of TCGA and GSE65858 cohorts,

@@

%
\begin{MyColorPar}{blue}
Answer
%(OK)

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We appreciate the reviewer for the critical comments.
feature selection => includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
# For example, a group of co-regulated genes that are preferable to be taken into consideration in select features.
 Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.

%Bayesian Hyper-LASSO Classification for Feature Selection with Application to HNSCC RNA-seq Data\cite{Jiang2020} -> citing \cite{Li2018d}
***We apply Bayesian Logistic Regression with Heavy-tailed Priors\cite{Li2018d} by R package HTLR (available at https://github.com/cran/HTLR) in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
HTLR utilize an Markov chain Monte Carlo (MCMC) method for learning multinomial logistic regression with hyper-LASSO priors. The MCMC algorithm uses Hamiltonian Monte Carlo in a restricted Gibbs sampling framework.

%X Bayesian Robit regression method with Hyper-LASSO priors (shortened by BayesHL) for feature selection in high dimensional genomic data with grouping structure.
%We apply BayesHL in gene expression analysis to identify subsets of genes that contribute to the overall survival outcome of HNSCC patients.
*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
% BayesHL is immune to the problem of correlation bias. Other convex and non-convex methods may not be able to identify significant features when there is a high number of correlated features, due to the problem of correlation bias

%coxlogit: https://www.info.ucl.ac.be/~pdupont/pdupont/pdf/MCDM_14.pdf
The Cox proportional hazard regression and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
Here we make use of both tasks by the Coxlogit mixed model.
As such this approach outperforms a Cox proportional hazard model or a logistic regression, each of those models being efficient essentially on their own task\cite{Branders2014}.
*** However, the LASSO has been criticized for being biased in gene selection, because it penalizes all the gene coefficients equally\cite{Fan2014}.
It could be overcame by assigning a consistent weight to each gene, which has been implemented in the adaptive LASSO (APLR)\cite{Algamal2015}\cite{Wu2018}.% was originally proposed to. 
accuracy from 95\% to 97\% :-)

***  a gene signature with deep learning CNN,
or http://gepia2.cancer-pku.cn/#index
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-020-03544-z
%https://bmcbioinformatics.biomedcentral.com/articles/10.1186/s12859-021-04040-8
or
% PCA of gene signature => L1/L2 penalized Cox model; L1-penalized (Lasso) Cox proportional hazard regression model (R package glmnet)
%x Statistical methods: Development of a 13-gene signature prediction model for survival in HPV-negative OSCC patients.
%To build a prediction model for OSCC-specific survival unique to the patients with HPV-negative OSCCs\cite{Lohavanichbutr2013}.
